---
title: "Face Word Projects -- Data Analysis"
author: "[Haiyang Jin](https://haiyangjin.github.io/)"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_depth: 6
    toc_float: 
      collapsed: true
      smooth_scroll: false
    includes:
      after_body: Utilities/footer.html
---

# Preparations
```{r general setting for this document, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)  # hide all warnings
knitr::opts_chunk$set(message = FALSE)  # hide all messages
showAll = FALSE
```

```{r preparation}
# load library
library(tidyverse)
library(afex)
library(lme4)
library(lmerTest)
library(emmeans)

```

# Load and clean data 
```{r assign filenames, include=showAll}
# assign filenames
fn_loc <- "FaceWord_Loc_Univariate.csv"
fn_univar <- "FaceWord_Univariate.csv"
fn_cosmo <- "FaceWord_CosmoMVPA.csv"
fn_simi <- "Main_Similarity.csv"  # similarity of top+bottom to intact vs. misconfigured. 

# set the order of levels in factors
locOrder <- c("face", "object", "word", "scrambled")

facewordOrder <- c("face", "word")
wordsOrder <- c("Chinese", "English")
layoutOrder <- c("intact", "exchange", "top", "bottom")
ROIOrder <- c("FFA", "FFA1", "FFA2", "VWFA", "LOC")

pairOrder_E1 <- c("face_intact-word_intact",
                  "face_intact-face_exchange",
                  "face_top-face_bottom",
                  "word_intact-word_exchange",
                  "word_top-word_bottom")
pairOrder_E2 <- c("Chinese_intact-English_intact",
                  "Chinese_intact-Chinese_exchange",
                  "Chinese_top-Chinese_bottom",
                  "English_intact-English_exchange",
                  "English_top-English_bottom")

# criterion of vertex number
nVtx_min <- 50


```

```{r setting for plots, include=showAll}
# set up the theme for plot and rainclound plot
# load all the R files in "Utilities/"
tmp <- sapply(list.files('Utilities', "*.R", full.names = TRUE, recursive = TRUE), source)

activationUL <- 2.75
onesample0 <- 0.3 # the staring point of y axis (for one-sample t-tests)
nDigitals <- 3 # number of digitials of p-values in plots
sig_size <- 5 # font size of p-values in plots

# function to obtain the p values for one-sample t-test
one_sig <- function(one_results, nDigitals = 4) {
  sig_vector <- signif(unlist(one_results["p.value",], use.names = FALSE), nDigitals)
  # sig_vector <- as.character(sig_vector)
  return(sig_vector)
}

```

## Data from localizer scans
```{r load data file from localizer scans for univerate analysis, include=showAll}
# load data file from localizer scans for univerate analysis
df_loc <- read_csv(fn_loc)

str(df_loc)
```

```{r clean the loc data, include=showAll}
df_clean_loc <- {
  df_loc %>% 
    rename(Label = ROI) %>% 
    mutate(Conditions = factor(Conditions, levels = locOrder)) %>% # convert Conditions to factors
    select(ExpCode, Label, SubjCode, Conditions, Resp) 
}

str(df_clean_loc)
```

## Data for univariate analyses
```{r load data file for univariate analysis, include=showAll}
# load data file from functional scans for univerate analysis
df_univar <- read_csv(fn_univar)

str(df_univar)
```

```{r clean the univariate data, include=showAll}
df_clean_univar <- {
  df_univar %>% 
    filter(nVertices >= nVtx_min) %>% # remove the label whose vertex number is smaller than nVtx_min
    separate(Conditions, c("FaceWord", "Layout"), "_") %>% # separate the conditions into two IVs
    mutate(# FaceWord = as.factor(FaceWord),
           Layout = factor(Layout, levels = layoutOrder), # convert the two IVs to factors
           Hemisphere = if_else(grepl("lh", Label), "left", if_else(grepl("rh", Label), "right", "NA"))) %>% 
    select(ExpCode, Hemisphere, Label, SubjCode, FaceWord, Layout, Resp) 
}

str(df_clean_univar)
```

```{r aggregate data for running anova, include=showAll}
df_univar_agg <- {
  df_clean_univar %>% 
    group_by(ExpCode, Hemisphere, Label, SubjCode, FaceWord, Layout) %>% 
    summarize(meanResp = mean(Resp), Count = n()) %>% 
    ungroup()
}

str(df_univar_agg)
```


## Data from CoSMoMVPA
```{r load data file from cosmoMVPA, include=showAll}
df_mvpa <- read_csv(fn_cosmo)

str(df_mvpa)
```

```{r clean the cosmomvpa data, include=showAll}
df_clean_mvpa <- {
  df_mvpa %>% 
    filter(nVertices >= nVtx_min) %>% # remove the label whose vertex number is smaller than nVtx_min
    select(ExpCode, Label, SubjCode, ClassifyPair, Predicted, Targets, ACC) %>% 
    mutate(Hemisphere = if_else(grepl("lh", Label), "left", if_else(grepl("rh", Label), "right", "NA")))
}

str(df_clean_mvpa)
```

```{r calculate accuracy for each condition, include=showAll}
df_mvpa_acc <- {
  df_clean_mvpa %>% 
    select(-c(Predicted, Targets)) %>% # remove these two columns
    group_by(ExpCode, Hemisphere, Label, SubjCode, ClassifyPair) %>% # divide the data into groups by these columns 
    summarize(Accuracy = mean(ACC), Count = n()) %>% 
    ungroup()
}
```

```{r descriptive analyses for mvpa, include=showAll}
desc_mvpa_acc <- {
  df_mvpa_acc %>% 
    group_by(ExpCode, Hemisphere, Label, ClassifyPair) %>% 
    summarize(emmean = mean(Accuracy), Count = n(), SE = sd(Accuracy)/sqrt(Count)) %>%
    mutate(lower.CL = lower_ci(emmean, SE, Count),
           upper.CL = upper_ci(emmean, SE, Count)) %>% 
    ungroup()
  }

```

## Data for the Similarity of top + bottom
```{r Data for the Similarity of top + bottom}
df_simi <- read_csv(fn_simi)

str(df_simi)
```

```{r clean the similarity data}

df_clean_simi <- {
  df_simi %>% 
    mutate(ClassPair_2 = gsub("exchange", "misconfigured", ClassPair_2),
           PredictCond = gsub("exchange", "misconfigured", PredictCond),
           asMiscon = if_else(grepl("misconfigured", PredictCond), 1, 0),
           pMiscon = Probability_2,
           ExpCode = if_else(grepl("facewordN", SubjCode), 2, 1))
}

str(df_clean_simi)
```

```{r rate of decoding as misconfigured}

df_rate_simi <- {
  df_clean_simi %>% 
    group_by(ExpCode, SubjCode, Labelname, ClassPair_1, Combination) %>% 
    summarize(RateAsMiscon = mean(asMiscon),
              pAsMiscon = mean(pMiscon)) %>% 
    ungroup() %>% 
    mutate(Hemisphere = if_else(grepl("lh", Labelname), 'left', if_else(grepl("rh", Labelname), "right", "NA")))
}

str(df_rate_simi)
```


# ROI information
```{r roi information, include=showAll}
# obtain from MVPA dataset
roi_info <- {
  df_mvpa %>% 
    filter(nVertices >= nVtx_min) %>% # remove the label whose vertex number is smaller than nVtx_min
    select(ExpCode, Label, SubjCode, nVertices, LabelSize) %>% 
    distinct()
}

# labels used in the analyses
label_list <- unique(roi_info$Label)

# logical (which condition these labels are)
isLeft <- grepl("lh", label_list) # is left hemisphere label
isRight <- grepl("rh", label_list) # is right hemisphere label

isFFA1 <- grepl("ffa1", label_list) # is FFA1
isFFA2 <- grepl("ffa2", label_list) # is FFA2
isVWFA <- grepl("w-vs-o", label_list) # is visual word form area
isLOC <- grepl("o-vs-scr", label_list) # is Lateral occipital cortex
isFFA <- !isFFA1 & !isFFA2 & !isVWFA & !isLOC

# labels for each ROI
label_lFFA <- label_list[isLeft & isFFA] # the labels for left FFA
label_rFFA <- label_list[isRight & isFFA] # the labels for right FFA
label_lFFA1 <- label_list[isLeft & isFFA1] # the labels for left FFA1
label_rFFA1 <- label_list[isRight & isFFA1] # the labels for left FFA1
label_lFFA2 <- label_list[isLeft & isFFA2] # the labels for left FFA2
label_rFFA2 <- label_list[isRight & isFFA2] # the labels for left FFA1
label_lVWFA <- label_list[isVWFA] # the labels for visual word form area
label_lLOC <- label_list[isLeft & isLOC] # the labels for left LOC
label_rLOC <- label_list[isRight & isLOC] # the labels for the right LOC

# all the labels available in this analysis
# label_list
```


## Label used for each ROI
```{r}
# Experiment 1
label_lFFA_E1 <- label_lFFA[1] # "roi.lh.f20.f-vs-o.label" "roi.lh.f40.f-vs-o.label"
label_rFFA_E1 <- label_rFFA[1] # "roi.rh.f20.f-vs-o.label" "roi.rh.f40.f-vs-o.label"

label_lFFA1_E1 <- label_lFFA1[1] # "roi.lh.f13.f-vs-o.ffa1.label" "roi.lh.f20.f-vs-o.ffa1.label"
label_rFFA1_E1 <- label_rFFA1[1] # "roi.rh.f13.f-vs-o.ffa1.label"

label_lFFA2_E1 <- label_lFFA2[1] # "roi.lh.f13.f-vs-o.ffa2.label"
label_rFFA2_E1 <- label_rFFA2[1] # "roi.rh.f20.f-vs-o.ffa2.label" "roi.rh.f40.f-vs-o.ffa2.label"

label_VWFA_E1 <- label_lVWFA[1] # "roi.lh.f13.w-vs-o.label"

label_lLOC_E1 <- label_lLOC[1] # "roi.lh.f13.o-vs-scr.label"
label_rLOC_E1 <- label_rLOC[1] # "roi.rh.f13.o-vs-scr.label"

# Experiment 2
label_lFFA_E2 <- label_lFFA[1] # "roi.lh.f20.f-vs-o.label" "roi.lh.f40.f-vs-o.label"
label_rFFA_E2 <- label_rFFA[1] # "roi.rh.f20.f-vs-o.label" "roi.rh.f40.f-vs-o.label"

label_lFFA1_E2 <- label_lFFA1[1] # "roi.lh.f13.f-vs-o.ffa1.label" "roi.lh.f20.f-vs-o.ffa1.label"
label_rFFA1_E2 <- label_rFFA1[1] # "roi.rh.f13.f-vs-o.ffa1.label"

label_lFFA2_E2 <- label_lFFA2[1] # "roi.lh.f13.f-vs-o.ffa2.label"
label_rFFA2_E2 <- label_rFFA2[1] # "roi.rh.f20.f-vs-o.ffa2.label" "roi.rh.f40.f-vs-o.ffa2.label"

label_VWFA_E2 <- label_lVWFA[1] # "roi.lh.f13.w-vs-o.label"

label_lLOC_E2 <- label_lLOC[1] # "roi.lh.f13.o-vs-scr.label"
label_rLOC_E2 <- label_rLOC[1] # "roi.rh.f13.o-vs-scr.label"

ROI <- factor(c("FFA", "FFA1", "FFA2", "VWFA", "LOC"), levels = ROIOrder)
left_E1 <- c(label_lFFA_E1, label_lFFA1_E1, label_lFFA2_E1, label_VWFA_E1, label_lLOC_E1)
right_E1 <- c(label_rFFA_E1, label_rFFA1_E1, label_rFFA2_E1, 'NA', label_rLOC_E1)
left_E2 <- c(label_lFFA_E2, label_lFFA1_E2, label_lFFA2_E2, label_VWFA_E2, label_lLOC_E2)
right_E2 <- c(label_rFFA_E2, label_rFFA1_E2, label_rFFA2_E2, 'NA', label_rLOC_E2)

label_ROI <- tibble("ROI" = ROI, "left_E1" = left_E1, "right_E1"= right_E1, "left_E2" = left_E2, "right_E2" = right_E2)

label_ROI
```

## Size of labels
```{r size (mm2) of labels for each subject}
roi_info %>% 
  select(-nVertices) %>% 
  spread(Label, LabelSize) 

```


## Number of vertices for each label
```{r}
roi_info %>% 
  select(-LabelSize) %>% 
  spread(Label, nVertices) 

```


## Number of subjects 
```{r number of subjects in for each label}
# desc_mvpa_acc %>% 
#   select(ExpCode, Label, Count) %>% 
#   distinct() %>%
#   spread(Label, Count) 

desc_mvpa_acc %>%
  select(ExpCode, Label, Count) %>% 
  distinct() %>% 
  filter(Label %in% c(left_E1, right_E1, left_E2, right_E2)) %>% 
  mutate(Hemi = substr(Label, 5,6),
         Hemisphere = if_else(Hemi == "lh", "left", if_else(Hemi == "rh", "right", "NA")),
         Col_name = paste(Hemisphere, paste0("E", ExpCode), sep = "_"),
         ROI = if_else(grepl("ffa1", Label), "FFA1", 
                       if_else(grepl("ffa2", Label), "FFA2", 
                               if_else(grepl("w-vs-o", Label), "VWFA", 
                                       if_else(grepl("o-vs-scr", Label), "LOC",
                                               "FFA")))), 
         ROI = factor(ROI, levels = ROIOrder)) %>% 
  select(ROI, Col_name, Count) %>% 
  spread(Col_name, Count) %>% 
  select(ROI, left_E1, right_E1, everything()) 
  
```

## Number of subjects excluded
```{r Number of subjects excluded}
# df_mvpa %>%
#   filter(nVertices < nVtx_min) %>% # remove the label whose vertex number is smaller than nVtx_min
#   select(ExpCode, Label, SubjCode) %>%
#   distinct() %>%
#   group_by(ExpCode, Label) %>%
#   summarize(Count = n()) %>%
#   ungroup() %>% 
#   spread(Label, Count)

df_mvpa %>%
  filter(nVertices < nVtx_min) %>% # remove the label whose vertex number is smaller than nVtx_min
  select(ExpCode, Label, SubjCode) %>%
  distinct() %>%
  group_by(ExpCode, Label) %>%
  summarize(Count = n()) %>% 
  ungroup() %>% 
  filter(Label %in% c(left_E1, right_E1, left_E2, right_E2)) %>% 
  mutate(Hemi = substr(Label, 5,6),
         Hemisphere = if_else(Hemi == "lh", "left", if_else(Hemi == "rh", "right", "NA")),
         Col_name = paste(Hemisphere, paste0("E", ExpCode), sep = "_"),
         ROI = if_else(grepl("ffa1", Label), "FFA1", 
                       if_else(grepl("ffa2", Label), "FFA2", 
                               if_else(grepl("w-vs-o", Label), "VWFA", 
                                       if_else(grepl("o-vs-scr", Label), "LOC",
                                               "FFA")))),
         ROI = factor(ROI, levels = ROIOrder)) %>%  
  select(ROI, Col_name, Count) %>% 
  spread(Col_name, Count) %>% 
  select(ROI, left_E1, right_E1, everything()) 
```


# Experiment 1: faces and words
## Localizer (Univariate analyses)
```{r only keep the univariate data for E1 loc}
df_loc_E1 <- {
  df_clean_loc %>%  
    filter(ExpCode == 1) %>% 
    mutate(SubjCode = as.factor(SubjCode))
}
# nlevels(df_loc_E1$SubjCode) # number of subjects
```
The ROI (label) used for this analysis is `r unique(df_loc_E1$LOC)`.

### rm-ANOVA
```{r}
anova_loc_E1 <- aov_4(Resp ~ Conditions + (Conditions | SubjCode), data = df_loc_E1)

anova_loc_E1
```

```{r estimated marginal means for loc E1}
emm_loc_anova_E1 <- emmeans(anova_loc_E1, ~ Conditions)

emm_loc_anova_E1
```

```{r Post-hoc analysis for anova loc E1}
contrast(emm_loc_anova_E1, "pairwise")

```

### Linear mixed model
```{r lmm for E1 loc}
lmm_loc_E1 <- lmer(Resp ~ Conditions + (1 | SubjCode), data = df_loc_E1)

summary(lmm_loc_E1)
```

```{r estimated marginal means for lmm loc E1}
emm_loc_lmm_E1 <- emmeans(lmm_loc_E1, ~ Conditions)

emm_loc_lmm_E1
```

```{r comparison among levels in Conditions lmm loc E1}
contrast(emm_loc_lmm_E1, "pairwise")
```

### Plot
```{r plots for loc E1 (anova), fig.asp=1.5}
plot_loc_E1 <- {
  ggplot(data = as.data.frame(emm_loc_anova_E1), aes(y = emmean, x = Conditions)) + # set the data, varialbes for x and y axises
    geom_col(position = "identity", color = "black", alpha = .7) +  # position of columns and countour of columns
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Stimuli", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    general_theme
}

plot_loc_E1
```


## Main runs
```{r only keep the univariate data for E1}
# only keep data of E1
df_univar_E1 <- {
  df_clean_univar %>% 
    filter(ExpCode == 1) %>% 
    mutate(FaceWord = factor(FaceWord, levels = facewordOrder),
           SubjCode = as.factor(SubjCode))
}

df_univar_agg_E1 <- {
  df_univar_agg %>% 
    filter(ExpCode == 1) %>% 
    mutate(FaceWord = factor(FaceWord, levels = facewordOrder),
           SubjCode = as.factor(SubjCode))
}

```

```{r only keep the multivariate (mvpa) data for E1}
# only keep data of E1
df_mvpa_E1 <- {
  df_clean_mvpa %>% 
    filter(ExpCode == 1) %>% 
    mutate(ClassifyPair = factor(ClassifyPair, levels = pairOrder_E1),
           SubjCode = as.factor(SubjCode))
}

df_mvpa_acc_E1 <- {
  df_mvpa_acc %>% 
    filter(ExpCode == 1) %>% 
    mutate(ClassifyPair = factor(ClassifyPair, levels = pairOrder_E1),
           SubjCode = as.factor(SubjCode))
}

desc_mvpa_acc_E1 <- {
  desc_mvpa_acc %>% 
    filter(ExpCode == 1) %>% 
    mutate(ClassifyPair = factor(ClassifyPair, levels = pairOrder_E1)) %>% 
    arrange(ExpCode, Hemisphere, Label, ClassifyPair) 
}

```

```{r only keep the similarity for E1}
df_rate_simi_E1 <- {
  df_rate_simi %>% 
    filter(ExpCode == 1) %>% 
    mutate(SubjCode = as.factor(SubjCode))
}

```


### Label:FFA
```{r the label used for FFA E1}
# label_lFFA_E1 <- label_lFFA[1] # "roi.lh.f20.f-vs-o.label" "roi.lh.f40.f-vs-o.label"
# label_rFFA_E1 <- label_rFFA[1] # "roi.rh.f20.f-vs-o.label" "roi.rh.f40.f-vs-o.label"

label_FFA_E1 <- c(label_lFFA_E1, label_rFFA_E1)

```
The label used for left FFA in Experiment 1 is *`r label_lFFA_E1`*. <br>
The label used for right FFA in Experiment 1 is *`r label_rFFA_E1`*.

```{r only keep data for FFA E1}
# only keep data for these two labels
df_univar_E1_FFA <- filter(df_univar_E1, Label %in% label_FFA_E1) 
df_univar_agg_E1_FFA <- filter(df_univar_agg_E1, Label %in% label_FFA_E1)
df_mvpa_E1_FFA <- filter(df_mvpa_E1, Label %in% label_FFA_E1)
df_mvpa_acc_E1_FFA <- filter(df_mvpa_acc_E1, Label %in% label_FFA_E1)
desc_mvpa_acc_E1_FFA <- filter(desc_mvpa_acc_E1, Label %in% label_FFA_E1)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E1_FFA %>% filter(Label == label_rFFA_E1))$SubjCode))

desc_mvpa_acc_E1_FFA %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
###### Left FFA
```{r anova for univariate E1 FFA left}
anova_E1_lFFA <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_FFA, Label == label_lFFA_E1))

anova_E1_lFFA
```

```{r estimated marginal means for univairate E1 lFFA}
emm_anova_E1_lFFA <- emmeans(anova_E1_lFFA, ~ FaceWord * Layout)

emm_anova_E1_lFFA %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_lFFA}
contrast(emmeans(emm_anova_E1_lFFA, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_lFFA, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_lFFA}
contr_anova_E1_lFFA <- contrast(emm_anova_E1_lFFA, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_lFFA
```

###### Right FFA
```{r anova for univariate E1 FFA right}
anova_E1_rFFA <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_FFA, Label == label_rFFA_E1))

anova_E1_rFFA
```

```{r estimated marginal means for univairate E1 FFA right}
emm_anova_E1_rFFA <- emmeans(anova_E1_rFFA, ~ FaceWord * Layout)

emm_anova_E1_rFFA %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_rFFA right}
contrast(emmeans(emm_anova_E1_rFFA, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_rFFA, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_rFFA right}
contr_anova_E1_rFFA <- contrast(emm_anova_E1_rFFA, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_rFFA
```

##### Plot
```{r plots for functional scans E1 (anova) FFA}

sig_uni_E1_FFA <- c(signif(as.data.frame(contr_anova_E1_lFFA)[c(5, 11), "p.value"], nDigitals), rep("", 6),
                     signif(as.data.frame(contr_anova_E1_rFFA)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E1_FFA <- sig_colors(sig_uni_E1_FFA)

# add the column of Hemisphere
nRow_E1 <-nrow(as.data.frame(emm_anova_E1_lFFA))
Hemisphere <- c(rep("left", nRow_E1), rep("right", nRow_E1))
desp_uni_E1_FFA <- cbind(Hemisphere, rbind(as.data.frame(emm_anova_E1_lFFA), as.data.frame(emm_anova_E1_rFFA)))

plot_uni_E1_FFA <- {
  ggplot(data = desp_uni_E1_FFA, aes(y = emmean, x = Hemisphere, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(FaceWord ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Hemisphere", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E1_FFA, color = color_uni_E1_FFA, size = sig_size, nudge_y = 0.5, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E1_FFA
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E1 lFFA}
df_mvpa_agg_E1_FFA <- {
  df_mvpa_acc_E1_FFA %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E1_lFFA <- {
  df_mvpa_agg_E1_FFA %>% 
    filter(Hemisphere == "left") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately
}

one_mvpa_agg_E1_lFFA
```

```{r one-sample for results of mvpa E1 rFFA}
one_mvpa_agg_E1_rFFA <- {
  df_mvpa_agg_E1_FFA %>% 
    filter(Hemisphere == "right") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}

one_mvpa_agg_E1_rFFA
```

##### Plot
```{r plots for functional scans mvpa E1 (anova) FFA}

sig_mvpa_agg_E1_FFA <- c(one_sig(one_mvpa_agg_E1_lFFA), one_sig(one_mvpa_agg_E1_rFFA))
color_uni_E1_FFA <- sig_colors(sig_mvpa_agg_E1_FFA)

plot_mvpa_E1_FFA <- {
  ggplot(data = desc_mvpa_acc_E1_FFA, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E1_FFA, color = color_uni_E1_FFA, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E1_FFA
```

#### Similarity of top + bottom to intact vs. misconfigured
##### One-sample t-test
```{r Similarity of top + bottom to intact vs. misconfigured in FFA}

one_simi_E1_FFA <- df_simi_rate_E1_FFA %>% 
    group_by(Hemisphere, Combination) %>% 
    summarize(mean = t.test(RateAsMiscon, mu = 0.5)[[5]],
              SD = t.test(RateAsMiscon, mu = 0.5)[[7]],
              t = t.test(RateAsMiscon, mu = 0.5)[[1]],
              df = t.test(RateAsMiscon, mu = 0.5)[[2]],
              p = round(t.test(RateAsMiscon, mu = 0.5)[[3]], 5),
              lower.CL = t.test(RateAsMiscon, mu = 0.5)[[4]][1],
              upper.CL = t.test(RateAsMiscon, mu = 0.5)[[4]][2],
              nullValue = t.test(RateAsMiscon, mu = 0.5)[[6]],
              alternative = t.test(RateAsMiscon, mu = 0.5)[[8]]
    )

one_simi_E1_FFA

```

##### Plot
```{r Similarity of top+bottom to intact vs. misconfigured in FFA, fig.height=3.5, fig.width=6}

plot_simi_E1_FFA <- {
  ggplot(data = one_simi_E1_FFA, aes(y = mean, x = Combination, fill = Combination)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "Similarity of top+bottom to intact vs. misconfigured in FFA", x = "Combinations", y = "Decoding as misconfigured") +  # set the names for main, x and y axises
    # geom_text(label = sig_mvpa_agg_E1_FFA, color = color_uni_E1_FFA, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}


plot_simi_E1_FFA
```


### Label:FFA1
```{r the label used for FFA1 E1}
# label_lFFA1_E1 <- label_lFFA1[1] # "roi.lh.f13.f-vs-o.ffa1.label" "roi.lh.f20.f-vs-o.ffa1.label"
# label_rFFA1_E1 <- label_rFFA1[1] # "roi.rh.f13.f-vs-o.ffa1.label"

label_FFA1_E1 <- c(label_lFFA1_E1, label_rFFA1_E1)

```
The label used for left FFA1 in Experiment 1 is *`r label_lFFA1_E1`*. <br>
The label used for right FFA1 in Experiment 1 is *`r label_rFFA1_E1`*.

```{r only keep data for FFA1 E1}
# only keep data for these two labels
df_univar_E1_FFA1 <- filter(df_univar_E1, Label %in% label_FFA1_E1) 
df_univar_agg_E1_FFA1 <- filter(df_univar_agg_E1, Label %in% label_FFA1_E1)
df_mvpa_E1_FFA1 <- filter(df_mvpa_E1, Label %in% label_FFA1_E1)
df_mvpa_acc_E1_FFA1 <- filter(df_mvpa_acc_E1, Label %in% label_FFA1_E1)
desc_mvpa_acc_E1_FFA1 <- filter(desc_mvpa_acc_E1, Label %in% label_FFA1_E1)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E1_FFA1 %>% filter(Label == label_rFFA1_E1))$SubjCode))

desc_mvpa_acc_E1_FFA1 %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
###### Left FFA1
```{r anova for univariate E1 FFA1 left}
anova_E1_lFFA1 <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_FFA1, Label == label_lFFA1_E1))

anova_E1_lFFA1
```

```{r estimated marginal means for univairate E1 lFFA1}
emm_anova_E1_lFFA1 <- emmeans(anova_E1_lFFA1, ~ FaceWord * Layout)

emm_anova_E1_lFFA1 %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_lFFA1}
contrast(emmeans(emm_anova_E1_lFFA1, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_lFFA1, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_lFFA1}
contr_anova_E1_lFFA1 <- contrast(emm_anova_E1_lFFA1, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_lFFA1
```

###### Right FFA1
```{r anova for univariate E1 FFA1 right}
anova_E1_rFFA1 <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_FFA1, Label == label_rFFA1_E1))

anova_E1_rFFA1
```

```{r estimated marginal means for univairate E1 FFA1 right}
emm_anova_E1_rFFA1 <- emmeans(anova_E1_rFFA1, ~ FaceWord * Layout)

emm_anova_E1_rFFA1 %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_rFFA1 right}
contrast(emmeans(emm_anova_E1_rFFA1, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_rFFA1, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_rFFA1 right}
contr_anova_E1_rFFA1 <- contrast(emm_anova_E1_rFFA1, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_rFFA1
```

##### Plot
```{r plots for functional scans E1 (anova) FFA1}

sig_uni_E1_FFA1 <- c(signif(as.data.frame(contr_anova_E1_lFFA1)[c(5, 11), "p.value"], nDigitals), rep("", 6),
                     signif(as.data.frame(contr_anova_E1_rFFA1)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E1_FFA1 <- sig_colors(sig_uni_E1_FFA1)

# add the column of Hemisphere
nRow_E1 <-nrow(as.data.frame(emm_anova_E1_lFFA1))
Hemisphere <- c(rep("left", nRow_E1), rep("right", nRow_E1))
desp_uni_E1_FFA1 <- cbind(Hemisphere, rbind(as.data.frame(emm_anova_E1_lFFA1), as.data.frame(emm_anova_E1_rFFA1)))

plot_uni_E1_FFA1 <- {
  ggplot(data = desp_uni_E1_FFA1, aes(y = emmean, x = Hemisphere, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(FaceWord ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Hemisphere", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E1_FFA1, color = color_uni_E1_FFA1, size = 5, nudge_y = 0.5, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E1_FFA1
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E1 lFFA1}
df_mvpa_agg_E1_FFA1 <- {
  df_mvpa_acc_E1_FFA1 %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E1_lFFA1 <- {
  df_mvpa_agg_E1_FFA1 %>% 
    filter(Hemisphere == "left") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E1_lFFA1
```

```{r one-sample for results of mvpa E1 rFFA1}
one_mvpa_agg_E1_rFFA1 <- {
  df_mvpa_agg_E1_FFA1 %>% 
    filter(Hemisphere == "right") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E1_rFFA1
```


##### Plot
```{r plots for functional scans mvpa E1 (anova) FFA1}

sig_mvpa_agg_E1_FFA1 <- c(one_sig(one_mvpa_agg_E1_lFFA1), one_sig(one_mvpa_agg_E1_rFFA1))
color_uni_E1_FFA1 <- sig_colors(sig_mvpa_agg_E1_FFA1)

plot_mvpa_E1_FFA1 <- {
  ggplot(data = desc_mvpa_acc_E1_FFA1, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E1_FFA1, color = color_uni_E1_FFA1, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E1_FFA1
```

### Label:FFA2
```{r the label used for FFA2 E1}
# label_lFFA2_E1 <- label_lFFA2[1] # "roi.lh.f13.f-vs-o.ffa2.label"
# label_rFFA2_E1 <- label_rFFA2[1] # "roi.rh.f20.f-vs-o.ffa2.label" "roi.rh.f40.f-vs-o.ffa2.label"

label_FFA2_E1 <- c(label_lFFA2_E1, label_rFFA2_E1)

```
The label used for left FFA2 in Experiment 1 is *`r label_lFFA2_E1`*. <br>
The label used for right FFA2 in Experiment 1 is *`r label_rFFA2_E1`*.

```{r only keep data for FFA2 E1}
# only keep data for these two labels
df_univar_E1_FFA2 <- filter(df_univar_E1, Label %in% label_FFA2_E1) 
df_univar_agg_E1_FFA2 <- filter(df_univar_agg_E1, Label %in% label_FFA2_E1)
df_mvpa_E1_FFA2 <- filter(df_mvpa_E1, Label %in% label_FFA2_E1)
df_mvpa_acc_E1_FFA2 <- filter(df_mvpa_acc_E1, Label %in% label_FFA2_E1)
desc_mvpa_acc_E1_FFA2 <- filter(desc_mvpa_acc_E1, Label %in% label_FFA2_E1)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E1_FFA2 %>% filter(Label == label_lFFA2_E1))$SubjCode))

desc_mvpa_acc_E1_FFA2 %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
###### Left FFA2
```{r anova for univariate E1 FFA2 left}
anova_E1_lFFA2 <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_FFA2, Label == label_lFFA2_E1))

anova_E1_lFFA2
```

```{r estimated marginal means for univairate E1 lFFA2}
emm_anova_E1_lFFA2 <- emmeans(anova_E1_lFFA2, ~ FaceWord * Layout)

emm_anova_E1_lFFA2 %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_lFFA2}
contrast(emmeans(emm_anova_E1_lFFA2, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_lFFA2, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_lFFA2}
contr_anova_E1_lFFA2 <- contrast(emm_anova_E1_lFFA2, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_lFFA2
```

###### Right FFA2
```{r anova for univariate E1 FFA2 right}
anova_E1_rFFA2 <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_FFA2, Label == label_rFFA2_E1))

anova_E1_rFFA2
```

```{r estimated marginal means for univairate E1 FFA2 right}
emm_anova_E1_rFFA2 <- emmeans(anova_E1_rFFA2, ~ FaceWord * Layout)

emm_anova_E1_rFFA2 %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_rFFA2 right}
contrast(emmeans(emm_anova_E1_rFFA2, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_rFFA2, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_rFFA2 right}
contr_anova_E1_rFFA2 <- contrast(emm_anova_E1_rFFA2, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_rFFA2
```

##### Plot
```{r plots for functional scans E1 (anova) FFA2}

sig_uni_E1_FFA2 <- c(signif(as.data.frame(contr_anova_E1_lFFA2)[c(5, 11), "p.value"], nDigitals), rep("", 6),
                     signif(as.data.frame(contr_anova_E1_rFFA2)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E1_FFA2 <- sig_colors(sig_uni_E1_FFA2)

# add the column of Hemisphere
nRow_E1 <-nrow(as.data.frame(emm_anova_E1_lFFA2))
Hemisphere <- c(rep("left", nRow_E1), rep("right", nRow_E1))
desp_uni_E1_FFA2 <- cbind(Hemisphere, rbind(as.data.frame(emm_anova_E1_lFFA2), as.data.frame(emm_anova_E1_rFFA2)))

plot_uni_E1_FFA2 <- {
  ggplot(data = desp_uni_E1_FFA2, aes(y = emmean, x = Hemisphere, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(FaceWord ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Hemisphere", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E1_FFA2, color = color_uni_E1_FFA2, size = 5, nudge_y = 0.5, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E1_FFA2
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E1 lFFA2}
df_mvpa_agg_E1_FFA2 <- {
  df_mvpa_acc_E1_FFA2 %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E1_lFFA2<- {
  df_mvpa_agg_E1_FFA2 %>% 
    filter(Hemisphere == "left") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E1_lFFA2
```

```{r one-sample for results of mvpa E1 rFFA2}
one_mvpa_agg_E1_rFFA2 <- {
  df_mvpa_agg_E1_FFA2 %>% 
    filter(Hemisphere == "right") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E1_rFFA2
```


##### Plot
```{r plots for functional scans mvpa E1 (anova) FFA2}

sig_mvpa_agg_E1_FFA2 <- c(one_sig(one_mvpa_agg_E1_lFFA2), one_sig(one_mvpa_agg_E1_rFFA2))
color_uni_E1_FFA2 <- sig_colors(sig_mvpa_agg_E1_FFA2)

plot_mvpa_E1_FFA2 <- {
  ggplot(data = desc_mvpa_acc_E1_FFA2, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E1_FFA2, color = color_uni_E1_FFA2, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E1_FFA2
```


### Label: left Visual Word Form Area (VWFA)
```{r the label used for VWFA E1}
# label_VWFA_E1 <- label_lVWFA[1] # "roi.lh.f13.w-vs-o.label"

```
The label used for (left) VWFA in Experiment 1 is *`r label_VWFA_E1`*.

```{r only keep data for VWFA E1}
# only keep data for these two labels
df_univar_E1_VWFA <- filter(df_univar_E1, Label %in% label_VWFA_E1) 
df_univar_agg_E1_VWFA <- filter(df_univar_agg_E1, Label %in% label_VWFA_E1)
df_mvpa_E1_VWFA <- filter(df_mvpa_E1, Label %in% label_VWFA_E1)
df_mvpa_acc_E1_VWFA <- filter(df_mvpa_acc_E1, Label %in% label_VWFA_E1)
desc_mvpa_acc_E1_VWFA <- filter(desc_mvpa_acc_E1, Label %in% label_VWFA_E1)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E1_VWFA %>% filter(Label == label_VWFA_E1))$SubjCode))

desc_mvpa_acc_E1_VWFA %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
```{r anova for univariate E1 VWFA left}
anova_E1_VWFA <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_VWFA, Label == label_VWFA_E1))

anova_E1_VWFA
```

```{r estimated marginal means for univairate E1 VWFA}
emm_anova_E1_VWFA <- emmeans(anova_E1_VWFA, ~ FaceWord * Layout)

emm_anova_E1_VWFA %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_VWFA}
contrast(emmeans(emm_anova_E1_VWFA, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_VWFA, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_VWFA}
contr_anova_E1_VWFA <- contrast(emm_anova_E1_VWFA, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_VWFA
```

##### Plot
```{r plots for functional scans E1 (anova) VWFA}

sig_uni_E1_VWFA <- c(signif(as.data.frame(contr_anova_E1_VWFA)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E1_VWFA <- sig_colors(sig_uni_E1_VWFA)

plot_uni_E1_VWFA <- {
  ggplot(data = as.data.frame(emm_anova_E1_VWFA), aes(y = emmean, x = FaceWord, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Stimuli", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E1_VWFA, color = color_uni_E1_VWFA, size = 5, nudge_y = 0.5, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E1_VWFA
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E1 VWFA}
df_mvpa_agg_E1_VWFA <- {
  df_mvpa_acc_E1_VWFA %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E1_VWFA <- {
  df_mvpa_agg_E1_VWFA %>% 
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E1_VWFA
```


##### Plot
```{r plots for functional scans mvpa E1 (anova) VWFA, fig.asp=1.5}

sig_mvpa_agg_E1_VWFA <- c(one_sig(one_mvpa_agg_E1_VWFA))
color_uni_E1_VWFA <- sig_colors(sig_mvpa_agg_E1_VWFA)

plot_mvpa_E1_VWFA <- {
  ggplot(data = desc_mvpa_acc_E1_VWFA, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(Hemisphere ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E1_VWFA, color = color_uni_E1_VWFA, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E1_VWFA
```


### Label:Lateral Occipital Cortex
```{r the label used for LOC E1}
# label_lLOC_E1 <- label_lLOC[1] # 
# label_rLOC_E1 <- label_rLOC[1] # 

label_LOC_E1 <- c(label_lLOC_E1, label_rLOC_E1)

```
The label used for left LOC in Experiment 1 is *`r label_lLOC_E1`*. <br>
The label used for right LOC in Experiment 1 is *`r label_rLOC_E1`*.

```{r only keep data for LOC E1}
# only keep data for these two labels
df_univar_E1_LOC <- filter(df_univar_E1, Label %in% label_LOC_E1) 
df_univar_agg_E1_LOC <- filter(df_univar_agg_E1, Label %in% label_LOC_E1)
df_mvpa_E1_LOC <- filter(df_mvpa_E1, Label %in% label_LOC_E1)
df_mvpa_acc_E1_LOC <- filter(df_mvpa_acc_E1, Label %in% label_LOC_E1)
desc_mvpa_acc_E1_LOC <- filter(desc_mvpa_acc_E1, Label %in% label_LOC_E1)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E1_LOC %>% filter(Label == label_lLOC_E1))$SubjCode))

desc_mvpa_acc_E1_LOC %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
###### Left LOC
```{r anova for univariate E1 LOC left}
anova_E1_lLOC <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_LOC, Label == label_lLOC_E1))

anova_E1_lLOC
```

```{r estimated marginal means for univairate E1 lLOC}
emm_anova_E1_lLOC <- emmeans(anova_E1_lLOC, ~ FaceWord * Layout)

emm_anova_E1_lLOC %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_lLOC}
contrast(emmeans(emm_anova_E1_lLOC, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_lLOC, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_lLOC}
contr_anova_E1_lLOC <- contrast(emm_anova_E1_lLOC, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_lLOC
```

###### Right LOC
```{r anova for univariate E1 LOC right}
anova_E1_rLOC <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E1_LOC, Label == label_rLOC_E1))

anova_E1_rLOC
```

```{r estimated marginal means for univairate E1 LOC right}
emm_anova_E1_rLOC <- emmeans(anova_E1_rLOC, ~ FaceWord * Layout)

emm_anova_E1_rLOC %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E1_rLOC right}
contrast(emmeans(emm_anova_E1_rLOC, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E1_rLOC, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E1_rLOC right}
contr_anova_E1_rLOC <- contrast(emm_anova_E1_rLOC, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E1, interaction = "pairwise") # , adjust = "none"
contr_anova_E1_rLOC
```

##### Plot
```{r plots for functional scans E1 (anova) LOC}

sig_uni_E1_LOC <- c(signif(as.data.frame(contr_anova_E1_lLOC)[c(5, 11), "p.value"], nDigitals), rep("", 6),
                     signif(as.data.frame(contr_anova_E1_rLOC)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E1_LOC <- sig_colors(sig_uni_E1_LOC)

# add the column of Hemisphere
nRow_E1 <-nrow(as.data.frame(emm_anova_E1_lLOC))
Hemisphere <- c(rep("left", nRow_E1), rep("right", nRow_E1))
desp_uni_E1_LOC <- cbind(Hemisphere, rbind(as.data.frame(emm_anova_E1_lLOC), as.data.frame(emm_anova_E1_rLOC)))

plot_uni_E1_LOC <- {
  ggplot(data = desp_uni_E1_LOC, aes(y = emmean, x = Hemisphere, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(FaceWord ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Hemisphere", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E1_LOC, color = color_uni_E1_LOC, size = 5, nudge_y = 0.5, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E1_LOC
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E1 lLOC}
df_mvpa_agg_E1_LOC <- {
  df_mvpa_acc_E1_LOC %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E1_lLOC <- {
  df_mvpa_agg_E1_LOC %>% 
    filter(Hemisphere == "left") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E1_lLOC
```

```{r one-sample for results of mvpa E1 rLOC}
one_mvpa_agg_E1_rLOC <- {
  df_mvpa_agg_E1_LOC %>% 
    filter(Hemisphere == "right") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E1_rLOC
```


##### Plot
```{r plots for functional scans mvpa E1 (anova) LOC}

sig_mvpa_agg_E1_LOC <- c(one_sig(one_mvpa_agg_E1_lLOC), one_sig(one_mvpa_agg_E1_rLOC))
color_uni_E1_LOC <- sig_colors(sig_mvpa_agg_E1_LOC)

plot_mvpa_E1_LOC <- {
  ggplot(data = desc_mvpa_acc_E1_LOC, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E1_LOC, color = color_uni_E1_LOC, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E1_LOC
```


# Experiment 2: Chinese and English
## localizer (Univariate analyses)
```{r only keep the univariate data for E2 loc}
df_loc_E2 <- {
  df_clean_loc %>% 
    filter(ExpCode == 2) %>% 
    mutate(SubjCode = as.factor(SubjCode))
}
# nlevels(df_loc_E2$SubjCode) # number of subjects
```

### rm-ANOVA
```{r}
anova_loc_E2 <- aov_4(Resp ~ Conditions + (Conditions | SubjCode), data = df_loc_E2)

anova_loc_E2
```

```{r estimated marginal means for loc E2}
emm_loc_anova_E2 <- emmeans(anova_loc_E2, ~ Conditions)

emm_loc_anova_E2
```

```{r Post-hoc analysis for anova loc E2}
contrast(emm_loc_anova_E2, "pairwise")
```

### Linear mixed model
```{r lmm for E2 loc}
lmm_loc_E2 <- lmer(Resp ~ Conditions + (1 | SubjCode), data = df_loc_E2)

summary(lmm_loc_E2)
```

```{r estimated marginal means for lmm loc E2}
emm_loc_lmm_E2 <- emmeans(lmm_loc_E2, ~ Conditions)

emm_loc_lmm_E2
```

```{r comparison among levels in Conditions lmm loc E2}
contrast(emm_loc_lmm_E2, "pairwise")
```

### Plot
```{r plots for loc E2 (anova), fig.asp=1.5}
plot_loc_E2 <- {
  ggplot(data = as.data.frame(emm_loc_anova_E2), aes(y = emmean, x = Conditions)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Stimuli", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    general_theme
}

plot_loc_E2
```


## Main runs
```{r only keep the univariate data for E2}
# only keep data of E2
df_univar_E2 <- {
  df_clean_univar %>% 
    filter(ExpCode == 2) %>% 
    mutate(FaceWord = factor(FaceWord, levels = wordsOrder),
           SubjCode = as.factor(SubjCode))
}

df_univar_agg_E2 <- {
  df_univar_agg %>% 
    filter(ExpCode == 2) %>% 
    mutate(FaceWord = factor(FaceWord, levels = wordsOrder),
           SubjCode = as.factor(SubjCode))
}

```

```{r only keep the multivariate (mvpa) data for E2}
# only keep data of E2
df_mvpa_E2 <- {
  df_clean_mvpa %>% 
    filter(ExpCode == 2) %>% 
    mutate(ClassifyPair = factor(ClassifyPair, levels = pairOrder_E2),
           SubjCode = as.factor(SubjCode))
}

df_mvpa_acc_E2 <- {
  df_mvpa_acc %>% 
    filter(ExpCode == 2) %>% 
    mutate(ClassifyPair = factor(ClassifyPair, levels = pairOrder_E2),
           SubjCode = as.factor(SubjCode))
}

desc_mvpa_acc_E2 <- {
  desc_mvpa_acc %>% 
    filter(ExpCode == 2) %>% 
    mutate(ClassifyPair = factor(ClassifyPair, levels = pairOrder_E2)) %>% 
    arrange(ExpCode, Hemisphere, Label, ClassifyPair)
}

```

### Label:FFA
```{r the label used for FFA E2}
# label_lFFA_E2 <- label_lFFA[1] # "roi.lh.f20.f-vs-o.label" "roi.lh.f40.f-vs-o.label"
# label_rFFA_E2 <- label_rFFA[1] # "roi.rh.f20.f-vs-o.label" "roi.rh.f40.f-vs-o.label"

label_FFA_E2 <- c(label_lFFA_E2, label_rFFA_E2)

```
The label used for left FFA in Experiment 2 is *`r label_lFFA_E2`*. <br>
The label used for right FFA in Experiment 2 is *`r label_rFFA_E2`*.

```{r only keep data for FFA E2}
# only keep data for these two labels
df_univar_E2_FFA <- filter(df_univar_E2, Label %in% label_FFA_E2) 
df_univar_agg_E2_FFA <- filter(df_univar_agg_E2, Label %in% label_FFA_E2)
df_mvpa_E2_FFA <- filter(df_mvpa_E2, Label %in% label_FFA_E2)
df_mvpa_acc_E2_FFA <- filter(df_mvpa_acc_E2, Label %in% label_FFA_E2)
desc_mvpa_acc_E2_FFA <- filter(desc_mvpa_acc_E2, Label %in% label_FFA_E2)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E2_FFA %>% filter(Label == label_lFFA_E2))$SubjCode))

desc_mvpa_acc_E2_FFA %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
###### Left FFA
```{r anova for univariate E2 FFA left}
anova_E2_lFFA <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_FFA, Label == label_lFFA_E2))

anova_E2_lFFA
```

```{r estimated marginal means for univairate E2 lFFA}
emm_anova_E2_lFFA <- emmeans(anova_E2_lFFA, ~ FaceWord * Layout)

emm_anova_E2_lFFA %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_lFFA}
contrast(emmeans(emm_anova_E2_lFFA, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_lFFA, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_lFFA}
contr_anova_E2_lFFA <- contrast(emm_anova_E2_lFFA, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_lFFA
```

###### Right FFA
```{r anova for univariate E2 FFA right}
anova_E2_rFFA <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_FFA, Label == label_rFFA_E2))

anova_E2_rFFA
```

```{r estimated marginal means for univairate E2 FFA right}
emm_anova_E2_rFFA <- emmeans(anova_E2_rFFA, ~ FaceWord * Layout)

emm_anova_E2_rFFA %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_rFFA right}
contrast(emmeans(emm_anova_E2_rFFA, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_rFFA, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_rFFA right}
contr_anova_E2_rFFA <- contrast(emm_anova_E2_rFFA, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_rFFA
```

##### Plot
```{r plots for functional scans E2 (anova) FFA}

sig_uni_E2_FFA <- c(signif(as.data.frame(contr_anova_E2_lFFA)[c(5, 11), "p.value"], nDigitals), rep("", 6),
                     signif(as.data.frame(contr_anova_E2_rFFA)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E2_FFA <- sig_colors(sig_uni_E2_FFA)

# add the column of Hemisphere
nRow_E2 <-nrow(as.data.frame(emm_anova_E2_lFFA))
Hemisphere <- c(rep("left", nRow_E2), rep("right", nRow_E2))
desp_uni_E2_FFA <- cbind(Hemisphere, rbind(as.data.frame(emm_anova_E2_lFFA), as.data.frame(emm_anova_E2_rFFA)))

plot_uni_E2_FFA <- {
  ggplot(data = desp_uni_E2_FFA, aes(y = emmean, x = Hemisphere, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(FaceWord ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(-0.2, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Hemisphere", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
     geom_text(label = sig_uni_E2_FFA, color = color_uni_E2_FFA, size = 5, nudge_y = 0.3, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E2_FFA
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E2 lFFA}
df_mvpa_agg_E2_FFA <- {
  df_mvpa_acc_E2_FFA %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E2_lFFA <- {
  df_mvpa_agg_E2_FFA %>% 
    filter(Hemisphere == "left") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_lFFA
```

```{r one-sample for results of mvpa E2 rFFA}
one_mvpa_agg_E2_rFFA <- {
  df_mvpa_agg_E2_FFA %>% 
    filter(Hemisphere == "right") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_rFFA
```


##### Plot
```{r plots for functional scans mvpa E2 (anova) FFA}

sig_mvpa_agg_E2_FFA <- c(one_sig(one_mvpa_agg_E2_lFFA), one_sig(one_mvpa_agg_E2_rFFA))
color_uni_E2_FFA <- sig_colors(sig_mvpa_agg_E2_FFA)

plot_mvpa_E2_FFA <- {
  ggplot(data = desc_mvpa_acc_E2_FFA, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E2_FFA, color = color_uni_E2_FFA, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E2_FFA
```


### Label:FFA1
```{r the label used for FFA1 E2}
# label_lFFA1_E2 <- label_lFFA1[1] # "roi.lh.f13.f-vs-o.ffa1.label" "roi.lh.f20.f-vs-o.ffa1.label"
# label_rFFA1_E2 <- label_rFFA1[1] # "roi.rh.f13.f-vs-o.ffa1.label"

label_FFA1_E2 <- c(label_lFFA1_E2, label_rFFA1_E2)

```
The label used for left FFA1 in Experiment 2 is *`r label_lFFA1_E2`*. <br>
The label used for right FFA1 in Experiment 2 is *`r label_rFFA1_E2`*.

```{r only keep data for FFA1 E2}
# only keep data for these two labels
df_univar_E2_FFA1 <- filter(df_univar_E2, Label %in% label_FFA1_E2) 
df_univar_agg_E2_FFA1 <- filter(df_univar_agg_E2, Label %in% label_FFA1_E2)
df_mvpa_E2_FFA1 <- filter(df_mvpa_E2, Label %in% label_FFA1_E2)
df_mvpa_acc_E2_FFA1 <- filter(df_mvpa_acc_E2, Label %in% label_FFA1_E2)
desc_mvpa_acc_E2_FFA1 <- filter(desc_mvpa_acc_E2, Label %in% label_FFA1_E2)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E2_FFA1 %>% filter(Label == label_rFFA1_E2))$SubjCode))

desc_mvpa_acc_E2_FFA1 %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
###### Left FFA1
```{r anova for univariate E2 FFA1 left}
anova_E2_lFFA1 <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_FFA1, Label == label_lFFA1_E2))

anova_E2_lFFA1
```

```{r estimated marginal means for univairate E2 lFFA1}
emm_anova_E2_lFFA1 <- emmeans(anova_E2_lFFA1, ~ FaceWord * Layout)

emm_anova_E2_lFFA1 %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_lFFA1}
contrast(emmeans(emm_anova_E2_lFFA1, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_lFFA1, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_lFFA1}
contr_anova_E2_lFFA1 <- contrast(emm_anova_E2_lFFA1, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_lFFA1
```

###### Right FFA1
```{r anova for univariate E2 FFA1 right}
anova_E2_rFFA1 <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_FFA1, Label == label_rFFA1_E2))

anova_E2_rFFA1
```

```{r estimated marginal means for univairate E2 FFA1 right}
emm_anova_E2_rFFA1 <- emmeans(anova_E2_rFFA1, ~ FaceWord * Layout)

emm_anova_E2_rFFA1 %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_rFFA1 right}
contrast(emmeans(emm_anova_E2_rFFA1, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_rFFA1, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_rFFA1 right}
contr_anova_E2_rFFA1 <- contrast(emm_anova_E2_rFFA1, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_rFFA1
```

##### Plot
```{r plots for functional scans E2 (anova) FFA1}

sig_uni_E2_FFA1 <- c(signif(as.data.frame(contr_anova_E2_lFFA1)[c(5, 11), "p.value"], nDigitals), rep("", 6),
                     signif(as.data.frame(contr_anova_E2_rFFA1)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E2_FFA1 <- sig_colors(sig_uni_E2_FFA1)

# add the column of Hemisphere
nRow_E2 <-nrow(as.data.frame(emm_anova_E2_lFFA1))
Hemisphere <- c(rep("left", nRow_E2), rep("right", nRow_E2))
desp_uni_E2_FFA1 <- cbind(Hemisphere, rbind(as.data.frame(emm_anova_E2_lFFA1), as.data.frame(emm_anova_E2_rFFA1)))

plot_uni_E2_FFA1 <- {
  ggplot(data = desp_uni_E2_FFA1, aes(y = emmean, x = Hemisphere, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(FaceWord ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Hemisphere", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E2_FFA1, color = color_uni_E2_FFA1, size = 5, nudge_y = 0.5, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E2_FFA1
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E2 lFFA1}
df_mvpa_agg_E2_FFA1 <- {
  df_mvpa_acc_E2_FFA1 %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E2_lFFA1 <- {
df_mvpa_agg_E2_FFA1 %>% 
  filter(Hemisphere == "left") %>%  
  select(-Hemisphere) %>% 
  sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_lFFA1
```

```{r one-sample for results of mvpa E2 rFFA1}
one_mvpa_agg_E2_rFFA1 <- {
  df_mvpa_agg_E2_FFA1 %>% 
    filter(Hemisphere == "right") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_rFFA1
```


##### Plot
```{r plots for functional scans mvpa E2 (anova) FFA1}

sig_mvpa_agg_E2_FFA1 <- c(one_sig(one_mvpa_agg_E2_lFFA1), one_sig(one_mvpa_agg_E2_rFFA1))
color_uni_E2_FFA1 <- sig_colors(sig_mvpa_agg_E2_FFA1)

plot_mvpa_E2_FFA1 <- {
  ggplot(data = desc_mvpa_acc_E2_FFA1, aes(y = emmean, x = ClassifyPair, fill=ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E2_FFA1, color = color_uni_E2_FFA1, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E2_FFA1
```

### Label:FFA2
```{r the label used for FFA2 E2}
# label_lFFA2_E2 <- label_lFFA2[1] # "roi.lh.f13.f-vs-o.ffa2.label"
# label_rFFA2_E2 <- label_rFFA2[1] # "roi.rh.f20.f-vs-o.ffa2.label" "roi.rh.f40.f-vs-o.ffa2.label"

label_FFA2_E2 <- c(label_lFFA2_E2, label_rFFA2_E2)

```
The label used for left FFA2 in Experiment 1 is *`r label_lFFA2_E2`*. <br>
The label used for right FFA2 in Experiment 1 is *`r label_rFFA2_E2`*.

```{r only keep data for FFA2 E2}
# only keep data for these two labels
df_univar_E2_FFA2 <- filter(df_univar_E2, Label %in% label_FFA2_E2) 
df_univar_agg_E2_FFA2 <- filter(df_univar_agg_E2, Label %in% label_FFA2_E2)
df_mvpa_E2_FFA2 <- filter(df_mvpa_E2, Label %in% label_FFA2_E2)
df_mvpa_acc_E2_FFA2 <- filter(df_mvpa_acc_E2, Label %in% label_FFA2_E2)
desc_mvpa_acc_E2_FFA2 <- filter(desc_mvpa_acc_E2, Label %in% label_FFA2_E2)

# subjects used for each hemisphere
unique(as.character((df_univar_agg_E2_FFA2 %>% filter(Label == label_rFFA2_E2))$SubjCode))

desc_mvpa_acc_E2_FFA2 %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
###### Left FFA2
```{r anova for univariate E2 FFA2 left}
anova_E2_lFFA2 <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_FFA2, Label == label_lFFA2_E2))

anova_E2_lFFA2
```

```{r estimated marginal means for univairate E2 lFFA2}
emm_anova_E2_lFFA2 <- emmeans(anova_E2_lFFA2, ~ FaceWord * Layout)

emm_anova_E2_lFFA2 %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_lFFA2}
contrast(emmeans(emm_anova_E2_lFFA2, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_lFFA2, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_lFFA2}
contr_anova_E2_lFFA2 <- contrast(emm_anova_E2_lFFA2, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_lFFA2
```

###### Right FFA2
```{r anova for univariate E2 FFA2 right}
anova_E2_rFFA2 <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_FFA2, Label == label_rFFA2_E2))

anova_E2_rFFA2
```

```{r estimated marginal means for univairate E2 FFA2 right}
emm_anova_E2_rFFA2 <- emmeans(anova_E2_rFFA2, ~ FaceWord * Layout)

emm_anova_E2_rFFA2 %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_rFFA2 right}
contrast(emmeans(emm_anova_E2_rFFA2, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_rFFA2, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_rFFA2 right}
contr_anova_E2_rFFA2 <- contrast(emm_anova_E2_rFFA2, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_rFFA2
```

##### Plot
```{r plots for functional scans E2 (anova) FFA2}

sig_uni_E2_FFA2 <- c(signif(as.data.frame(contr_anova_E2_lFFA2)[c(5, 11), "p.value"], nDigitals), rep("", 6),
                     signif(as.data.frame(contr_anova_E2_rFFA2)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E2_FFA2 <- sig_colors(sig_uni_E2_FFA2)

# add the column of Hemisphere
nRow_E2 <-nrow(as.data.frame(emm_anova_E2_lFFA2))
Hemisphere <- c(rep("left", nRow_E2), rep("right", nRow_E2))
desp_uni_E2_FFA2 <- cbind(Hemisphere, rbind(as.data.frame(emm_anova_E2_lFFA2), as.data.frame(emm_anova_E2_rFFA2)))

plot_uni_E2_FFA2 <- {
  ggplot(data = desp_uni_E2_FFA2, aes(y = emmean, x = Hemisphere, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(FaceWord ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(-0.1, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Hemisphere", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E2_FFA2, color = color_uni_E2_FFA2, size = sig_size, nudge_y = 0.3, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E2_FFA2
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E2 lFFA2}
df_mvpa_agg_E2_FFA2 <- {
  df_mvpa_acc_E2_FFA2 %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E2_lFFA2 <- {
  df_mvpa_agg_E2_FFA2 %>% 
    filter(Hemisphere == "left") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_lFFA2
```

```{r one-sample for results of mvpa E2 rFFA2}
one_mvpa_agg_E2_rFFA2 <- {
  df_mvpa_agg_E2_FFA2 %>% 
    filter(Hemisphere == "right") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_rFFA2
```


##### Plot
```{r plots for functional scans mvpa E2 (anova) FFA2}

sig_mvpa_agg_E2_FFA2 <- c(one_sig(one_mvpa_agg_E2_lFFA2), one_sig(one_mvpa_agg_E2_rFFA2))
color_uni_E2_FFA2 <- sig_colors(sig_mvpa_agg_E2_FFA2)

plot_mvpa_E2_FFA2 <- {
  ggplot(data = desc_mvpa_acc_E2_FFA2, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E2_FFA2, color = color_uni_E2_FFA2, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E2_FFA2
```


### Label: left Visual Word Form Area (VWFA)
```{r the label used for VWFA E2}
# label_VWFA_E2 <- label_lVWFA[1] # "roi.lh.f13.w-vs-o.label"

```
The label used for (left) VWFA in Experiment 1 is *`r label_VWFA_E2`*.

```{r only keep data for VWFA E2}
# only keep data for these two labels
df_univar_E2_VWFA <- filter(df_univar_E2, Label %in% label_VWFA_E2) 
df_univar_agg_E2_VWFA <- filter(df_univar_agg_E2, Label %in% label_VWFA_E2)
df_mvpa_E2_VWFA <- filter(df_mvpa_E2, Label %in% label_VWFA_E2)
df_mvpa_acc_E2_VWFA <- filter(df_mvpa_acc_E2, Label %in% label_VWFA_E2)
desc_mvpa_acc_E2_VWFA <- filter(desc_mvpa_acc_E2, Label %in% label_VWFA_E2)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E2_VWFA %>% filter(Label == label_VWFA_E2))$SubjCode))

desc_mvpa_acc_E2_VWFA %>%
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
```{r anova for univariate E2 VWFA left}
anova_E2_VWFA <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_VWFA, Label == label_VWFA_E2))

anova_E2_VWFA
```

```{r estimated marginal means for univairate E2 VWFA}
emm_anova_E2_VWFA <- emmeans(anova_E2_VWFA, ~ FaceWord * Layout)

emm_anova_E2_VWFA %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_VWFA}
contrast(emmeans(emm_anova_E2_VWFA, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_VWFA, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_VWFA}
contr_anova_E2_VWFA <- contrast(emm_anova_E2_VWFA, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_VWFA
```

##### Plot
```{r plots for functional scans E2 (anova) VWFA}

sig_uni_E2_VWFA <- c(signif(as.data.frame(contr_anova_E2_VWFA)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E2_VWFA <- sig_colors(sig_uni_E2_VWFA)

plot_uni_E2_VWFA <- {
  ggplot(data = as.data.frame(emm_anova_E2_VWFA), aes(y = emmean, x = FaceWord, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(-0.3, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Stimuli", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E2_VWFA, color = color_uni_E2_VWFA, size = 5, nudge_y = 0.5, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E2_VWFA
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E2 VWFA}
df_mvpa_agg_E2_VWFA <- {
  df_mvpa_acc_E2_VWFA %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E2_lVWFA <- {
  df_mvpa_agg_E2_VWFA %>% 
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_lVWFA
```


##### Plot
```{r plots for functional scans mvpa E2 (anova) VWFA, fig.asp=1.5}

sig_mvpa_agg_E2_VWFA <- one_sig(one_mvpa_agg_E2_lVWFA)
color_uni_E2_VWFA <- sig_colors(sig_mvpa_agg_E2_VWFA)

plot_mvpa_E2_VWFA <- {
  ggplot(data = desc_mvpa_acc_E2_VWFA, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(Hemisphere ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E2_VWFA, color = color_uni_E2_VWFA, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E2_VWFA
```

### Label:Lateral Occipital Cortex
```{r the label used for LOC E2}
# label_lLOC_E2 <- label_lLOC[1] # 
# label_rLOC_E2 <- label_rLOC[1] # 

label_LOC_E2 <- c(label_lLOC_E2, label_rLOC_E2)

```
The label used for left LOC in Experiment 1 is *`r label_lLOC_E2`*. <br>
The label used for right LOC in Experiment 1 is *`r label_rLOC_E2`*.

```{r only keep data for LOC E2}
# only keep data for these two labels
df_univar_E2_LOC <- filter(df_univar_E2, Label %in% label_LOC_E2) 
df_univar_agg_E2_LOC <- filter(df_univar_agg_E2, Label %in% label_LOC_E2)
df_mvpa_E2_LOC <- filter(df_mvpa_E2, Label %in% label_LOC_E2)
df_mvpa_acc_E2_LOC <- filter(df_mvpa_acc_E2, Label %in% label_LOC_E2)
desc_mvpa_acc_E2_LOC <- filter(desc_mvpa_acc_E2, Label %in% label_LOC_E2)

# subjects used for each hemisphere
# unique(as.character((df_univar_agg_E2_LOC %>% filter(Label == label_lLOC_E2))$SubjCode))

desc_mvpa_acc_E2_LOC %>% 
  select(ExpCode, Label, Count) %>% 
  distinct()
```

#### Univariate analyses
##### rm-ANOVA 
###### Left LOC
```{r anova for univariate E2 LOC left}
anova_E2_lLOC <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_LOC, Label == label_lLOC_E2))

anova_E2_lLOC
```

```{r estimated marginal means for univairate E2 lLOC}
emm_anova_E2_lLOC <- emmeans(anova_E2_lLOC, ~ FaceWord * Layout)

emm_anova_E2_lLOC %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_lLOC}
contrast(emmeans(emm_anova_E2_lLOC, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_lLOC, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_lLOC}
contr_anova_E2_lLOC <- contrast(emm_anova_E2_lLOC, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_lLOC
```

###### Right LOC
```{r anova for univariate E2 LOC right}
anova_E2_rLOC <- aov_4(meanResp ~ FaceWord * Layout + (1 + FaceWord * Layout | SubjCode), 
                      data = filter(df_univar_agg_E2_LOC, Label == label_rLOC_E2))

anova_E2_rLOC
```

```{r estimated marginal means for univairate E2 LOC right}
emm_anova_E2_rLOC <- emmeans(anova_E2_rLOC, ~ FaceWord * Layout)

emm_anova_E2_rLOC %>% 
  as.data.frame() %>% 
  arrange(FaceWord)
```

```{r post-hoc for emm_anova_E2_rLOC right}
contrast(emmeans(emm_anova_E2_rLOC, ~ FaceWord), "pairwise")

contrast(emmeans(emm_anova_E2_rLOC, ~ Layout), "pairwise") # , adjust = "none"
```

```{r simple effect analyses for emm_anova_E2_rLOC right}
contr_anova_E2_rLOC <- contrast(emm_anova_E2_rLOC, "pairwise", simple = "each", combine = TRUE, adjust = "none")
# contrast(emm_uni_anova_E2, interaction = "pairwise") # , adjust = "none"
contr_anova_E2_rLOC
```

##### Plot
```{r plots for functional scans E2 (anova) LOC}

sig_uni_E2_LOC <- c(signif(as.data.frame(contr_anova_E2_lLOC)[c(5, 11), "p.value"], nDigitals), rep("", 6),
                     signif(as.data.frame(contr_anova_E2_rLOC)[c(5, 11), "p.value"], nDigitals), rep("", 6))
color_uni_E2_LOC <- sig_colors(sig_uni_E2_LOC)

# add the column of Hemisphere
nRow_E2 <-nrow(as.data.frame(emm_anova_E2_lLOC))
Hemisphere <- c(rep("left", nRow_E2), rep("right", nRow_E2))
desp_uni_E2_LOC <- cbind(Hemisphere, rbind(as.data.frame(emm_anova_E2_lLOC), as.data.frame(emm_anova_E2_rLOC)))

plot_uni_E2_LOC <- {
  ggplot(data = desp_uni_E2_LOC, aes(y = emmean, x = Hemisphere, fill = Layout)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(FaceWord ~ .) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    scale_y_continuous(expand= c(0, 0), limits = c(0, activationUL), breaks = seq(0, 3, .5)) +  # remove the space between columns and x axis
    labs(title = "", x = "Hemisphere", y = "Beta values") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_uni_E2_LOC, color = color_uni_E2_LOC, size = 5, nudge_y = 0.5, nudge_x = -0.25) + # add starts to the significant columns
    general_theme
}

plot_uni_E2_LOC
```


#### Multivarate analyses (MVPA)

##### One-sample t-test
```{r one-sample for results of mvpa E2 lLOC}
df_mvpa_agg_E2_LOC <- {
  df_mvpa_acc_E2_LOC %>% 
  spread(ClassifyPair, Accuracy) %>% # change to table (each row is one subject)
  select(-c(ExpCode, Label, SubjCode, Count)) # remove these columns
}

one_mvpa_agg_E2_lLOC <- {
  df_mvpa_agg_E2_LOC %>% 
    filter(Hemisphere == "left") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_lLOC
```

```{r one-sample for results of mvpa E2 rLOC}
one_mvpa_agg_E2_rLOC <- {
  df_mvpa_agg_E2_LOC %>% 
    filter(Hemisphere == "right") %>%  
    select(-Hemisphere) %>% 
    sapply(function(x) t.test(x, mu = 0.5, alternative = "greater")) # apply one-sample t-test to each column separately 
}
one_mvpa_agg_E2_rLOC
```


##### Plot
```{r plots for functional scans mvpa E2 (anova) LOC}

sig_mvpa_agg_E2_LOC <- c(one_sig(one_mvpa_agg_E2_lLOC), one_sig(one_mvpa_agg_E2_rLOC))
color_uni_E2_LOC <- sig_colors(sig_mvpa_agg_E2_LOC)

plot_mvpa_E2_LOC <- {
  ggplot(data = desc_mvpa_acc_E2_LOC, aes(y = emmean, x = ClassifyPair, fill = ClassifyPair)) + # set the data, varialbes for x and y axises
    geom_col(position = "dodge", color = "black", alpha = .7) +  # position of columns and countour of columns
    facet_grid(. ~ Hemisphere) +
    geom_errorbar(mapping = aes(ymin = lower.CL, ymax = upper.CL), linetype = 1,  # set the error bar
                  show.legend = FALSE, width = 0.25, alpha = .5,
                  position = position_dodge(width=0.9)) +
    geom_hline(yintercept = c(0.5, 1), linetype = 5, alpha = 0.5) +  # add the line for 0.5 and 1 (y)
    scale_y_continuous(expand= c(0, 0), limits = c(0, 1.1), breaks = seq(0, 1, .25)) +  # remove the space between columns and x axis
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + # show x labels in two rows
    labs(title = "", x = "Classification Pairs", y = "Accuracy") +  # set the names for main, x and y axises Subjective Responses for E205
    geom_text(label = sig_mvpa_agg_E2_LOC, color = color_uni_E2_LOC, size = sig_size, nudge_y = 0.15) + # add starts to the significant columns
    general_theme +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.line = element_line(size = 3))
    # theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1), # 
    #       axis.line = element_line(size = 3)) 
}

plot_mvpa_E2_LOC
```


# Versions of packages used
```{r versions}
# rstudioapi::versionInfo()
sessionInfo()
```
